---
title: "Linear Regression Simulation"
output: pdf_document
---
Simulate data
```{r}
set.seed(1)
windows(width=10, height=8)
x = rnorm(100)
eps = rnorm(100, 0, 0.25)
y = -1 + 0.5*x + eps
plot(x,y)
```
There is a linear relationship between x and y. They are positively correlated.


Predict y using x.
```{r}
windows(width=10, height=8)
x = rnorm(100)
eps = rnorm(100, 0, 0.25)
y = -1 + 0.5*x + eps
plot(x,y)
fit1= lm(y~x)
abline(coef(fit1))
```
The beta estimates are very close to the actual parameter. However, beta1 is statistically significantly different from 0.5.


Scatterplot:
```{r}
windows(width=10, height=8)
x<- rnorm(100)
eps<- rnorm(100, 0, 0.25)
y<- -1 + 0.5*x + eps
plot(x,y)
fit1<- lm(y~x)
abline(coef(fit1))
abline(-1,0.5,col = 'red',lty = 2)
legend('topleft',
       legend = c("OLS regression","Population regression"),
       col = c('black','red'),
       lty = 1:2, cex = 0.8,
       )
```



Polynomial regression
```{r}
fit2= lm(y~x+I(x^2))
summary(fit2)
```
It does not help because the R-sqaured decreases.



Less noise approach:
```{r}
windows(width=10, height=8)
x3 = rnorm(100)
eps= rnorm(100, 0, 0.1)
y3 = -1 + 0.5*x3 + eps
plot(x3,y3)
fit3= lm(y3~x3)
summary(fit3)
abline(coef(fit3))
abline(-1,0.5,col = 'red',lty = 2)
legend('topleft',
       legend = c("OLS regression","Population regression"),
       col = c('black','red'),
       lty = 1:2, cex = 0.8,
)
```
The estimated and actual regression line is almost identical.


More noise approach:
```{r}
windows(width=10, height=8)
x4 = rnorm(100)
eps = rnorm(100, 0, 0.5)
y4 = -1 + 0.5*x4 + eps
plot(x4,y4)
fit4= lm(y4~x4)
summary(fit4)
abline(coef(fit4))
abline(-1,0.5,col = 'red',lty = 2)
legend('topleft',
       legend = c("OLS regression","Population regression"),
       col = c('black','red'),
       lty = 1:2, cex = 0.8,
)
```
The estimates are less accurate because they have lower t value. The R-squared is lower.



```{r}
confint(fit1)
confint(fit3)
confint(fit4)
```
The width of confidence interval with noisier data is higher. 

